Trends of downward SDR in Thessaloniki

### 2023-05-09 Article.Rmd
Commit 2023-05-09 12:17
Commit 2023-05-10 00:17

panderOptions("table.alignment.default", "left")
pander(pp,
       caption = "\\label{tab:trendseasontable}Trends of daily means by sky conditions for the season of the year.")
```
\normalsize

@@

@@

```{r cumsumCLEAR, echo=F, fig.cap="Donditions."}
knitr::include_graphics("./images/CumulativeDailyCumSum-5.pdf")
```

>>>>

# panderOptions("table.alignment.default", "left")
panderOptions("table.alignment.default", "center")
pander(pp,
       caption = "\\label{tab:trendseasontable}Trends of daily means by sky conditions for the season of the year.")
```
\normalsize

@@

A method to evaluate changes in the long term trend is to use the cumulative sum of the variable.

@@

<!-- Not showing this trend -->
```{r cumsumCLEAR, echo=F, fig.cap="Donditions.", include=FALSE}
knitr::include_graphics("./images/CumulativeDailyCumSum-5.pdf")
```
